Forecasting the Support of Kamala Harris in 2024 U.S. Presidential Election using a Model-Based Approach with Poll-of-Polls Data

### 2024-11-04 paper/ForecastingtheSupportofKamalaHarrisin2024U.S.PresidentialElection.qmd
update paper with grammer error

In our analysis and shown result, we find out that the use of a weighted model helps to reduce volatility in predicted support trends by assigning greater importance to polls that are both recent and based on larger sample sizes. This approach effectively smooths out abrupt fluctuations that might otherwise result from older or smaller polls, providing a more stable and coherent view of voter sentiment. hough our data was filtered with recent polls after Harris's candidacy announcement, voter sentiment remains fluid, with ongoing debates and events likely to influence preferences. By emphasizing recent polls, the model is more responsive to the latest shifts in public opinion, which is especially relevant as election day approaches and voters’ preferences may crystallize. Larger-sample polls, often conducted by established pollsters like Siena/NYT or Emerson, are assumed to be more reliable, and their increased weight in the model further reduces the likelihood of erratic changes driven by smaller, less consistent polls. This decreased volatility allows the model to present a clearer picture of the general support trend for each candidate, reducing noise and highlighting true shifts in sentiment. However, this smoothing effect may also mask some of the localized or short-term dynamics captured by less frequent or smaller-sample polls, which could provide a unique understanding of specific voter groups or state-level shifts.

>>>>

In our analysis and shown result, we find out that the use of a weighted model helps to reduce volatility in predicted support trends by assigning greater importance to polls that are both recent and based on larger sample sizes. This approach effectively smooths out abrupt fluctuations that might otherwise result from older or smaller polls, providing a more stable and coherent view of voter sentiment. Though our data was filtered with recent polls after Harris's candidacy announcement, voter sentiment remains fluid, with ongoing debates and events likely to influence preferences. By emphasizing recent polls, the model is more responsive to the latest shifts in public opinion, which is especially relevant as election day approaches and voters’ preferences may crystallize. Larger-sample polls, often conducted by established pollsters like Siena/NYT or Emerson, are assumed to be more reliable, and their increased weight in the model further reduces the likelihood of erratic changes driven by smaller, less consistent polls. This decreased volatility allows the model to present a clearer picture of the general support trend for each candidate, reducing noise and highlighting true shifts in sentiment. However, this smoothing effect may also mask some of the localized or short-term dynamics captured by less frequent or smaller-sample polls, which could provide a unique understanding of specific voter groups or state-level shifts.
